### 2017-04-12 CS798-ConvexityAndOptimization/assignments/project.tex
starting in on describing ad auctions

If we looks at Step $2a$ of $\cA$, we observe multiplicative update rule very similar to those used in the study of the Multiplicative Weights Update Method of Lecture $9$:

@@

\subsection{Single Slot}

\subsection{Multiple Slots}
\bibliography{references}
\bibliographystyle{plain}
\end{document}

>>>>

If we looks at Step $2a$ of $\cA$, we observe a multiplicative update rule very similar to those used in the study of the Multiplicative Weights Update Method of Lecture $9$:

@@

The business of displaying ads in search engine results is a natural and important application for online algorithms. Search provides like Google and Microsoft will sell ad space to advertisers in the search results corresponding with some users given keyword query. The way they sell the space is through auctions to buyers interested in displaying ads related to the given query.

\subsection{Single Slot}
\paragraph{}
In the $\textit{ad-auctions problem}$ we are given a set $I$ of $n$ buyers, each with a daily budget of $B(i)$. We are also given a set $M$ of items with $|M| = m$. The items arrive in an online manner. Upon the arrival of some item, say the $j$-th item for $j \in [m]$, each buyer will submit a bid for said item, denoted $b(i,j)$. The algorithm can decide to allocate the item to any of the buyer upon its arrival. The online constraint is that they cannot reallocate items once they have decided who they are to be allocated to.
\paragraph{}
Allocations can be either $\textit{fractional}$ or $\textit{integral}$. In integral allocation, each item is allocated to a single buyer. In fractional allocations the items can be subdivided and allocated to multiple buyers. The algorithm we present will give an integral allocation, but the linear programming formulation we base it on will be fractional. Clearly, integral allocations suffice as fractional allocations, so we can naturally come our integral solutions to the optimal values of the fractional linear programs.
\paragraph{}
The objective is to maximize the total revenue of the seller. The revenue received from each buyer is the minimum of the sum total of bids corresponding to items allocated to that buyer and their budget. It is defined as such since we cannot overcharge buyers.
\subsection{Multiple Slots}
\bibliography{references}
\bibliographystyle{plain}
\end{document}
